Dynamical Properties of Molecular Cloud Complexes in a Redshift 6 Prototypical Galaxy at the Epoch of Reionization

### 2018-09-07 WRITEUP/ms.tex
typesetting

% --------------------------------------------
% \documentclass[twocolumn]{aastex6}
\documentclass[apj]{emulateapj} %iop
\usepackage{amsmath}

@@

\begin{abstract}
We study the dynamical properties of molecular clouds complexes and their temporal evolution in a prototypical galaxy 
at the Epoch of Reionization using state-of-the-art cosmological zoom-in simulation, 
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify molecular complexes (MC) and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in gas-rich galaxies in the local universe and at the peak epoch of cosmic \SF. 
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely results from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
% consistent with what has been found previously in higher resolution isolated simulation (our zoom-in sim here allows us to examine 
% the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM).
We compare the dynamics of MCs in \flower to those observed in the local Universe in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the 
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with ALMA will be useful to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}

>>>>

% --------------------------------------------
% \documentclass[twocolumn]{aastex6}
% \documentclass[apj]{emulateapj}
\documentclass[iop]{emulateapj} %iop
\usepackage{amsmath}

@@

\begin{abstract}
We study the dynamical properties of molecular clouds complexes and their temporal evolution in a prototypical galaxy 
at the Epoch of Reionization (EoR) using state-of-the-art cosmological zoom-in simulation, 
which includes a chemical network to determine the formation of molecular
hydrogen, heating and cooling of the ISM by metals, and stellar feedback.
We use a clump finder algorithm and a set of H$_2$ volumetric densities ($n_{\rm cut}$) 
to identify molecular complexes (MC) and their sub-structures.
We extract properties such as mass, size, Mach number, velocity dispersion, gas surface density, and virial parameter for each MC.
We find that the MC of \flower are highly supersonic, with high velocity dispersions ($\sigma\approx$\,200\,\kms) comparable to 
those observed in gas-rich galaxies in the local universe and at the peak epoch of cosmic \SF. 
The mass scale of the MCs is of the order of $10^{6.5-9}$\,\Msun. The $\sim$200\,pc-scale MCs found with a low density threshold 
correspond to the arms of the disk of \flower which break down into smaller $\lesssim$100\,pc-scale MCs at higher density thresholds. 
The more massive and bigger MCs in \flower compared to the Milky Way 
likely results from the higher gas mass fraction, surface density, and velocity dispersion, 
which set the scale for fragmentation.
% consistent with what has been found previously in higher resolution isolated simulation (our zoom-in sim here allows us to examine 
% the influence on the dynamics of MCs due to continuous gas accretion from the surrounding IGM).
We compare the dynamics of MCs in \flower to those observed in the local Universe in the context of the Larson's relation.
The MCs of \flower are found to have higher $\sigma$ and $\Sigma$ systematically regardless of the $n_{\rm cut}$ adopted.
The velocity dispersion remains $\gtrsim$100\,\kms even when we increase the $n_{\rm cut}$ and even for the 
the molecular substructures, likely resulting from 
the strong supernova and stellar feedback \flower experienced over the multiple episodes of bursty \SF.
Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter. 
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are 
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}$\ssim1 for the MCs in the satellite galaxies, which we interpret as a result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower (also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures. This paints a picture, in which at the EoR, \SF continues 
as gas is being accreted from the IGM.
We find no temporal variations in the MC dynamics over the course of 700\,Myr traced in our simulation, at least in terms of the scaling relations examined. 
Our results are independent of the volume density threshold adopted, except for the slope of the cumulative 
mass distribution, which steepens as we increase $n_{\rm cut}$. 
High resolution imaging of the first galaxies with ALMA will be useful to test our findings and the validity of our simulation to shed
light on \SF since the cosmic dark ages.
\end{abstract}
\keywords{methods: data analysis --
          galaxies: high-redshift --
          galaxies: ISM --
          galaxies: evolution --
          galaxies: formation --
          galaxies: starburst --
          stars: formation}
